Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Rewrite "Growable" section.

Children grow. To accommodate them, Nell provides a ``low floor and
no ceiling.''  A very simple base system provides the low
floor, usable with no literacy skills or
external guidance.  The serial progression of story modules grows with
the child to tackle topics of increasing difficulty.
Later, the ability for third
parties to independently author story modules ensures that
Nell can continue to grow.  Finally, there are no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

We also seek to eliminate the ``ceiling'' between the children and
the authors of the Nell system itself.  Nell should be capable of
teaching about itself, and a capable child can dive into Nell's source
code and make meaningful changes.
%In Section~\ref{sec:turtles} we describe how this goal is approached.

%%% XXX INTEGRATE THIS SECTION XXX
Nell is implemented in standard Web technologies, including HTML5,
WebGL, and JavaScript, with extensive use of offline caching.
Resources are named by URL, even when disconnected from the
internet.  This allows third parties to manage their own namespaces
when extending Nell, and simplifies updates to story modules and
the Nell system itself.
%As far as possible, Nell is implemented in JavaScript.
% if the kid's going to learn some software stack, this seem like a
% fine one to learn

>>>>

Children grow.  Nell aims to provide a ``low floor and no ceiling'' to
grow with them, along three main axes.
%There are three main axes of growth.
%  Nell's low floor is its
%simple base system,
%usable with no literacy skills or external guidance.
%From there Nell grows in three directions.

First, Nell tracks the child's growing intelligence and capability
with increasingly challenging story material.  As the child
accumulates achievements and demonstrates
proficiency, the serial story moves on to more advanced topics.

Second, Nell seeks to grow its authoring community.  Decentralized
authorship ensures that Nell's instructional content
will continue to grow, with an increasing number of topics and
customizations.  There are no
ceilings barring a child from participating: Nell
contains a story editor and everything necessary to
author and publish story modules.

To further promote collaboration
Nell is implemented in standard Web technologies (HTML5,
WebGL, and JavaScript) with offline caching.
Resources are named by URL, even when disconnected from the
internet, which simplifies the distribution of updates to story modules and
the Nell system.  URL-based naming allows third parties
to manage their own namespaces when extending Nell.

Finally, Nell is designed to allow a capable child to learn
the construction of the system itself,
eliminating the ceiling between the child and
the authors of the Nell system.  Nell can teach
about itself, and its source code is open for exploration within Nell.
Meaningful changes can be performed without external tools.

%.  Meaningful changes to the Nell system can
%be performed on the system itself.
%In Section~\ref{sec:turtles} we describe how this goal is approached.

%As far as possible, Nell is implemented in JavaScript.
% if the kid's going to learn some software stack, this seem like a
% fine one to learn
